---
title: "Lab-R Character Manipulation"
author: "Michael Robinson"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"
```{r cars}

library(readr)
library(dplyr)

# Reading data from website.
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv"

# Load the dataset from the url
college_majors <- read_csv(url)

# Filter majors that contain "DATA" or "STATISTICS"
filtered_majors <- college_majors %>%
  filter(grepl("DATA|STATISTICS", Major, ignore.case = TRUE))

# Show the majors that meet the specified criteria.
filtered_majors

```
# 2.Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:
c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
# Create a string vector 
fruit_data <- c('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"')

# Eliminate line identifiers and square brackets.
new_fruit_vector <- gsub("\\[\\d+\\] |\\n", "", fruit_data)

# Segment the string using double quotes as separators.
new_fruit_vector <- unlist(strsplit(new_fruit_vector, '\\"'))

# Filtering for only letters 
new_fruit_vector <- new_fruit_vector[grep("[a-z]", new_fruit_vector)]

# Print the result
print(new_fruit_vector)

comp_data <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
# Print the result

comp_data
```
# 3.  Describe, in words, what these expressions will match:


1. `(.)\1\1`:  Matches three consecutive characters that are all the same.

2. `"(.)(.)\\2\\1"`: Matches any four character string where the first and last characters are the same, and the middle two characters are also the same. 

3. `(..)\1`: Matches any four character string where the first two characters are the same as the last two characters.

4. `"(.).\\1.\\1"`: Matches any five character string that the first and  the third character are the same, and the third and fifth character are the same. 

5. `"(.)(.)(.).*\\3\\2\\1"`: Matches a string that begins with three characters in any order, followed by any number of characters, and ends with those same three characters in reverse order.

# 4. Construct regular expressions to match words that:

  a.) Start and end with the same character. "^(.).*\\1$"
  b.) Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)                    ".*(.)\\1.*\\1.*"
  c.) Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
        ".*(.)\\1\\1\\1.*"


